Random Forest to find the top important features

### 2019-11-01 scripts/17_RF_CR_find_top_features copy.Rmd
update

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = F, warning = F)
library(randomForest)
library(ggpubr)
library(tidyverse)
library(kableExtra)
```

## Response to Toxicity

@@

```{r}
tox_RF <- randomForest(s_tb_rf, factor(pheno$Toxicity), importance = T)

@@

combined_tox_RF <- randomForest(formula = Toxicity ~ ., data = combined,  importance = T )

@@

combined_tox_RF_fil <- randomForest(formula = Toxicity ~ ., data = combined_fil,  importance = T )

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = F, warning = F)
library(randomForest)
library(ggpubr)
library(tidyverse)
library(kableExtra)
library(arrangements)
library(caret)
```

## Response to CR

@@

```{r}
tox_RF <- randomForest(s_tb_rf, factor(pheno$CR), importance = T)

@@

combined_tox_RF <- randomForest(formula = CR ~ ., data = combined,  importance = T )

@@

combined_tox_RF_fil <- randomForest(formula = CR ~ ., data = combined_fil,  importance = T , ntree = 1000 )

@@

```{r}
# to use the top N percent features

# to test on different threshold of selecting most abundant species
sum_thre <- seq(0.5, 1, 0.05)
tree_num <- 1000

res <- sum_thre %>% 
  set_names(sum_thre) %>% 
  map(function(thre) {
    s_sum_top <- quantile(s_sum, thre)
    combined_fil <- cbind(s_tb_rf[,names(s_sum[s_sum > s_sum_top])], pheno %>% 
                    select(-Sampleid))

    tibble(
      num_fea = length(s_sum[s_sum > s_sum_top]) ,
      OOB_err_rate = randomForest(formula = CR ~ ., data = combined_fil,  importance = T , ntree = tree_num )[['err.rate']][tree_num, 1]

    ) 
  }) %>% 
  bind_rows(.id = 'thre')
```

Interesting, using no feature info actually has smaller OOB error rate.

```{r}
# try different combination of pheno to predict. (doesn't seem they are correlated right?)
# select 2 out of 4 pheno vars other than CR
all_var <- names(pheno)
combi <- combinations(all_var[!all_var %in% c('Sampleid','CR')], 2) %>% 
  as.data.frame(stringsAsFactors = F)

phe_table <- apply(combi, 1, function(Row) {
  phe_fil = pheno %>% 
    select(CR, Row[['V1']], Row[['V2']])
})

# use those tables to do a random forest
phe_fil_res <- phe_table %>% 
  map(function(tbl) {
     tibble(
      OOB_err_rate = randomForest(formula = CR ~ ., data = tbl,  importance = T , ntree = tree_num )[['err.rate']][tree_num, 1]
    ) 
  }) %>% 
  bind_rows() %>% 
  bind_cols(combi) %>% 
  mutate(phe_combi = str_glue('CR_{V1}_{V2}')) %>% 
  select(-V1 , -V2) %>% 
  arrange(desc(OOB_err_rate))

# so the combi with the smallest error rate is:
phe_fil_res %>% 
  slice(which.min(OOB_err_rate)) %>% 
  pull(phe_combi)

# Is there correlation in the pheno table between CR and Disease_Class?
phe_2 <- pheno  %>% 
  select(CR, Disease_Class) %>% 
  mutate(Disease_Class = if_else(as.character(Disease_Class) == 'CD19 Malignancy', 'CD19', 'Multi')) %>% 
  table()

chi2 <-  chisq.test(phe_2)
chi2$p.value # reject the null hypothesis of independence

# CR and ORR
phe_2 <- pheno  %>% 
  select(CR, ORR)  %>% 
  table()

chi2 <-  chisq.test(phe_2)
chi2$p.value # reject the null hypothesis of independence

# so they are actually correlated
```
